Asteroid shape reconstruction

### 2018-03-23 abstract.tex
Working on outline

\begin{itemize}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
    \item The surface shape is necessary in order to allow the spacecraft to operate near the surface of the a steroid
        \begin{itemize}
            \item The polyhedron potential model is a function of the shape and highly dependent on an accurate shape model.
            \item It is not possible to accurately determine the shape of the asteroid from ground based measurements.
                Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
            \item The shape is
        \end{itemize}
\end{itemize}
